gap' issue

### 2017-06-13 analysis/ObjGap.rmd
Files commited by wflow_commit.

---
title: "'gap' issue"
author: "Wei Wang"
date: 
output: html_document
---

@@

@@

```{r}
rank1test_0(1,60,100,1,0.6,1,0.5)
```

## Session information

>>>>

---
title: "'gap' issue"
author: "Wei Wang"
date: 2017-06-12
output: html_document
---

@@

#### special case

```{r}
rank1test(1,10,200,0.5,0.6,1,1)
```

this case

```{r}
rank1test(1,10,200,0.5,0.5,1,3)
```

this case show that the `shink` and `uniform + point mass` are not same.

```{r}
rank1test(1,10,200,0.5,0.5,1,2.5)
```

In this case, `fdr` method tend to get rank zero estimation, which has highest value of objective function, but rank one model with `spike and slab` has better performance in prediction.

@@

```{r}
rank1test_0(1,60,100,1,0.6,1,0.5)
```
test
## Session information
